%-------------------------
  % Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------
  
  \documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
  % Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
    }
  }
  
  \newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-5pt}
      }
      
      \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
        
        \renewcommand{\labelitemii}{$\circ$}
        
        \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
        \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
        \newcommand{\resumeItemListStart}{\begin{itemize}}
        \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
        
        %-------------------------------------------
          %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
          
          
          \begin{document}
        
        %----------HEADING-----------------
          \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\href{http://shyambv.com/}{\Large Shyam BV}} & Email : \href{mailto:shyambv86@gmail.com}{shyambv86@gmail.com}\\
        \href{https://www.linkedin.com/in/shyambv/}{Linkedin}/\href{https://bvshyam.medium.com/}{Medium}/\href{https://github.com/bvshyam}{Github}/\href{https://shyambv.com}{Website} & Mobile : +1-908-838-8800 \\
        \end{tabular*}
        
        
        %-----------EDUCATION-----------------
          \section{Education}
        \resumeSubHeadingListStart
        \resumeSubheading
        {City University of New York}{New York, NY}
        {Master in Data Science;  GPA: 4.00}{}
        \resumeSubheading
        {Anna University}{Chennai, India}
        {Bachelor of Engineering in Electrical and Electronics;  GPA: 3.43}{}
        \resumeSubheading
        {National Institute of Information Technology}{Trichy, India}
        {Diploma in in Information Technology;}{}
        \resumeSubHeadingListEnd

        %-----------EXPERIENCE-----------------
          \section{Experience}
        \resumeSubHeadingListStart
        \resumeSubheading
        {Equifax - Data Scientist}{Atlanta, GA}
        {Customer facing Data Scientist}{Sep 2018 - Present}
                 \resumeItemListStart
        \resumeItem{Identity and Fraud - Attributes and Models}
        {Creating fraud attributes using PII's and models using the attributes.}
        \resumeItem{Identity and Fraud - Graph}
        {Created graph attributes to find fraudulent accounts using PII's in Equifax and execute it large scale.}
%         \resumeItem{Creating models/scores}
%         {Created models on propensity to buy and scoring for customers using Equifax dataset}
%          \resumeItemListEnd
        \resumeItem{Ignite Direct - Models}
        {Helping Equifax customers to solve their analytics use cases with various Equifax data assets. Created models on propensity to buy and scoring for customers.}
         \resumeItemListEnd

        \resumeSubheading
        {Multidimensions - Self-employment }{Atlanta, GA}
        {Solopreneur}{Feb 2020 - Present}
         \resumeItemListStart
          \resumeItem{Code Sprout}
        {A medium and substack blog to publish different articles on applications of code.}
        \resumeItem{Socialimageai.com}
        {AI marketing product for startups to create social media posts, articles from website or context using GPT-2, image recognition }
        \resumeItem{Sproutquik.xyz - Retired}
        {Created a product for startups to get up and run quickly. Similar to AWS amplify. Platform is built using terrafrom and AWS. }
         \resumeItem{Buildtheresume.com}
        {Product to create professional resume using OpenAI GPT-3 to create resume and perform resume QA using sentiment and transformer models. }
        
        \resumeItem{tradeslybot.com - Retired}
        {Customer facing chatbot via social media channels(Whatsapp, FB, Telegram) to trade and provide information on Stocks. }
         \resumeItemListEnd


        \resumeSubheading
        {Deutsche Bank - Data Scientist}{Cary, NC}
        {Assistant Vice President}{Sep 2014 - Sep 2018}
        \resumeItemListStart
        \resumeItem{Fraud Detection}
        {Replacing the existing rule-based system by analytics application to perform anomaly and fraud detection in the retail banking. Created models(parametric/non-parametric) and architect the
complete pipeline for the real-time application.}
        \resumeItem{Texas Oil Estimation}
        {Created seasonal estimation models using ARIMA/Prophet/Neural Networks to predict
the output in Texas oil wells and provide recommendations.}
                \resumeItem{COE - QA system}
        {Created QA(Chatbot) using Deep learning toolkit to address the common questions in
Center of Excellence team.}
                \resumeItem{Internal Documents classification}
        {Classified Deutsche Bank internal document classification from Enterprise
content management system using ensemble models and Neural networks.}
                \resumeItem{Credit/Operational Risk}
        {Developed credit/operational risk-based models and building a data pipeline using
Cloudera data science workbench. Also, migrated existing SAS based risk models to pyspark.}
        \resumeItemListEnd
        
        \resumeSubheading
        {Tata Consultancy Services - Sr. Data Analyst}{Edison, NJ}
        {AIG - Consultant}{Mar 2011 - Sep 2014}
        \resumeItemListStart
        \resumeItem{ISG Cost Containment}
        {Performed various data analysis/mining activities and expenses by applications.
Created models to predict the risk and expected over-expenses.}
        \resumeItem{DWFIT}
        {Worked as a Data Engineer to build data pipelines for an enterprise-wide Financial Information
Transparency Data warehousing system on Hadoop.}
        \resumeItem{Financial Information Transparency Budgeting}
        {Performed data analyst role by creating different forecast/budgeting cost-based models.}
  \resumeItemListEnd
  
        \resumeSubheading
        {Sensiple Softwares - System engineer}{}
        {Data Engineer}{Jul 2008 - Mar 2011}
        \resumeItemListStart
        \resumeItem{West Connect}
        {Performed analysis of voice metrics analysis and created various KPI's and metrics with Business
intelligence tools.}
        \resumeItem{Mileage Plus}
        {Performed ETL transformations on the mileage plus voice application from transactional to OLAP
database.}
        \resumeItem{Katana}
        {Worked on an OTC bond market trading application using core Java. It is a real-time trading application for banks and brokers.}

        \resumeItemListEnd
        \resumeSubHeadingListEnd
        
        
        %-----------Technical Skills-----------------
          \section{Technical Skills}
        \resumeSubHeadingListStart
        \resumeSubItem{Programming/Scripting}
        {Python, Java Script, Web Development, PLSQL}
        \resumeSubItem{ML}
        {Pytorch, Computer Vision, NLP, Machine Learning, Deep Learning, SparkML, H2O}
        \resumeSubItem{Data Engineering/DevOps}
        {Terraform, Hadoop, PySpark, Docker, Cloudera Data Science Workbench, CICD, AWS, GCP}
        \resumeSubItem{Visualizations/Databases}
        {Tableau, Qlikivew, BO, Cognos, Neo4j, Oracle, AWS DynamoDB}
        \resumeSubItem{Stat/Math/Others}
        {Statistical analysis, Regression, A/B tests}
                \resumeSubItem{Management}
        {Founded companies called 'Stainwash'(Retired) and 'Multidimensions'}

        \resumeSubHeadingListEnd
        
        %
        %--------PROGRAMMING SKILLS------------
          %\section{Programming Skills}
        %  \resumeSubHeadingListStart
        %    \item{
          %      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
          %      \hfill
          %      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
          %    }
        %  \resumeSubHeadingListEnd
        
        
        %-------------------------------------------
          \end{document}
        
